---
title: "W3_R"
author: "Mauricio Sanchez"
date: "November 15, 2015"
output: html_document
---

Objective: To study the dataset and the associated description of the data (i.e. “data dictionary”). You may need
to look around a bit, but it’s there! You should take the data, and create a data frame with a subset of the columns
(and if you like rows) in the dataset. You should include the column that indicates edible or poisonous and three or
four other columns. You should also add meaningful column names and replace the abbreviations used in the
data—for example, in the appropriate column, “e” might become “edible.” Your deliverable is the R code to
perform these transformation tasks

1. Scrape data and save it to a csv file:
```{r}
thisURL <- "https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.data";
mushroomData <- read.table(thisURL, header = FALSE, sep=",", stringsAsFactors = FALSE );
write.table(mushroomData, file = "mushroom_data.csv", sep = ",");
```

2. Read in CSV file into mushroom :

```{r, echo=TRUE}
mushroomData <- read.table("mushroom_data.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE);
head(mushroomData);
```

3. Study small data set and translate columns names
```{r, echo=TRUE}
mushroomData <- mushroomData[1:10, c(1, 2, 22, 23)];
names(mushroomData) <- c("class", "cap-shape", "population", "habitat");
head(mushroomData)

# translate class
levels(mushroomData$'class') <- c(levels(mushroomData$'class'), "edible", "poisonous")
mushroomData$'class'[mushroomData$'class' == 'e'] <- "edible"
mushroomData$'class'[mushroomData$'class' == 'p'] <- "poisonous"

# translate cap-shape
levels(mushroomData$'cap-shape') <- c(levels(mushroomData$'cap-shape'), "fibrous", "grooves", "scaly", "smooth")
mushroomData$'cap-shape'[mushroomData$'cap-shape' == 'b'] <- "bell"
mushroomData$'cap-shape'[mushroomData$'cap-shape' == 'c'] <- "conical"
mushroomData$'cap-shape'[mushroomData$'cap-shape' == 'x'] <- "convex"
mushroomData$'cap-shape'[mushroomData$'cap-shape' == 'f'] <- "flat"
mushroomData$'cap-shape'[mushroomData$'cap-shape' == 'k'] <- "knobbed"
mushroomData$'cap-shape'[mushroomData$'cap-shape' == 's'] <- "sunken"

# translate population
levels(mushroomData$'population') <- c(levels(mushroomData$'population'), "abundant", "clustered", "numerous", "scattered", "several", "solitary")
mushroomData$'population'[mushroomData$'population' == 'a'] <- "abundant"
mushroomData$'population'[mushroomData$'population' == 'c'] <- "clustered"
mushroomData$'population'[mushroomData$'population' == 'n'] <- "numerous"
mushroomData$'population'[mushroomData$'population' == 's'] <- "scattered"
mushroomData$'population'[mushroomData$'population' == 'v'] <- "several"
mushroomData$'population'[mushroomData$'population' == 'y'] <- "solitary"

# translate habitat
levels(mushroomData$'habitat') <- c(levels(mushroomData$'habitat'), "grasses", "leaves", "meadows", "paths", "urban", "waster", "woods")
mushroomData$'habitat'[mushroomData$'habitat' == 'g'] <- "grasses"
mushroomData$'habitat'[mushroomData$'habitat' == 'l'] <- "leaves"
mushroomData$'habitat'[mushroomData$'habitat' == 'm'] <- "meadows"
mushroomData$'habitat'[mushroomData$'habitat' == 'p'] <- "paths"
mushroomData$'habitat'[mushroomData$'habitat' == 'u'] <- "urban"
mushroomData$'habitat'[mushroomData$'habitat' == 'w'] <- "waster"
mushroomData$'habitat'[mushroomData$'habitat' == 'd'] <- "woods"

```

4. Print full translated data set
```{r, echo=TRUE}
print(mushroomData)
```
